### 2017-09-09 paper/evaluation.tex
Incorporated some comments from @damorim

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, and we were unable to test
\SubjectsGithubNotTestable{} projects  due to incompatible environment
(\eg, missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
``flaky tests''~\cite{luo-etal-fse2014}.
In general, a ``flaky test'' is a test that either pass or fail under
the same circumstances leading to non-deterministic results.
\Comment{While there are several causes that may introduce randomness on test
results, our concern is on flakiness caused by
parallel execution.}
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
\Jbc{From the \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with more than \SuiteFailingThreshold{} of tests failing to
reduce bias in our dataset.}
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

@@

It is important to note that we under-estimated cost in our
experiments for one main reason.
Some projects may omit long-running tests on their default
execution. For instance, the project \CodeIn{apache.maven-surefire}
runs all unit tests in a few seconds.  According to our criteria, this
project is classified as \shortg{} but a closer look reveals
that only smoke tests are run by default in this project.
Time-consuming integration and system tests are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.
\Jbc{
Although failing tests may introduce noise in our measurements, we
carefully eliminated subjects with more than \SuiteFailingThreshold{} of
test failures. 
From the \numSubjs{} testable projects, \numSubjsPass{} successfully
executed all tests and \numSubjsFail{} reported some test failure.
Furthermore, from these \numSubjsFail{} subjects, only 11 subjects
have more than 5\% of failing tests (7.3\% in average).
}
\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, nearly 1 in every 4
      projects) take at least 1 minute to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
measures the distribution of test costs in test suites as to estimate
(lack of) potential of obtaining speedups with parallelization.  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions. X-axis
        denote projects appearing in arbitrary order.}%
\end{figure}

@@

The dimension adoption focuses on the usage of parallelism in
open-source projects.  It evaluates (\numRQAdoptionOne) how often open-source
projects use parallelization schemes and (\numRQAdoptionTwo) how developers
involved in costly projects, not using parallelization, perceive this
technology.

\begin{itemize}
    \item \numRQAdoptionOne. \textbf{\RQAdoptionOne{}}
\end{itemize}

@@

which parallel configuration modes it will use to actually run the

@@

Table~\ref{tab:freqmodes-dynamic} shows the projects we identified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, three modules (=28-25) from Log4J2
use sequential configuration.

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.

\subsubsection{Static checking}
\label{sec:rqC-2}
Given the inherent limitation of dynamic monitoring to find evidence
of parallelism, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those case, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can occur when
\emph{pom.xml} files are encapsulated in jar files or downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.
Overall, we found, using this methodology, \numProjectsParStatic{}
projects that use parallelism.
Compared to the set of projects listed in
Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration \ParClassParMeth), \CodeIn{Mapstruct} (using configuration
\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
and \CodeIn{Takes} were not detected using this methodology.
That happened because these projects loaded a \emph{pom.xml} file from
a jar file that we did not check.  Considering the static and dynamic
methods together, we found a total of \numProjectsParTotal{} distinct
projects using parallelism, corresponding to the union of the two
subject sets.

@@

\begin{enumerate}
\item How long does it take for tests to run in your environment? Can
  you briefly define your setup?
\item Do you confirm that your regression test suite does *not* run in parallel?
\item\label{questionThree} Select a reason for not using parallelization:
  \begin{enumerate}[label=\alph*)]
  \item I did not know it was possible
  \item I was concerned with concurrency issues
  \item I use a continuous integration server
  \item Some other reason. Please elaborate.
  \end{enumerate}
\end{enumerate}

%% \begin{enumerate}
%% 	\item How long does it take for test to run in your
%%		environment?
%%	\item Can you briefly define your setup?
%%	\item Do you confirm that your project does not run in
%%		parallel?
%%	\item Select a reason for not using paralellization:
%%		\begin{enumarate}
%%			\item I did not know it was possible;
%%			\item I was concerned with concurrency issues;
%%			\item I use a continuous integration server;
%%			\item Some other reason.
%%		\end{enumerate}
%% \end{enumerate}
%% One of the goals of the first questions is to identify potential
%% discrepancies between our experimental environment and the environment
%% of developers.  Overall, we found that \Fix{...}

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites are modularized and
those modules are tested independently in CI servers through different
parameters.  Those participants explained that such practice helps to
reduce time to observe test failures, which is the goal of speeding up
regression testing.  A total of \emailsLocal{} participants answered
that they do run tests in their local machines.  Note, however, that
CI does not preclude low-level parallelization.  For example,
installations of open-source CI tools (\eg{}, Jenkins~\cite{jenkins})
in dedicated servers would benefit from running tests faster through
low-level test suite parallelization.

% \emailsNotDescribed{} developers did not described their environment.

Considering question 2, the answers we collected indicated, to our
surprise, that six of the \emailsProjectsAnswered{} projects execute
tests in parallel.  This mismatch is justified by cases where neither
of our checks (static or dynamic) could detect presence of
parallelism.  A closer look at these projects revealed that one of
them contained a \emph{pom.xml} file encapsulated in a jar file
(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
projects the participant considered that distributed CI was a form of
parallelism, and in four projects the team preferred to implement
parallelization instead of using existing features from the testing
framework and the build system~---~in two projects the team
implemented concurrency control with custom JUnit test runners and in
two other projects the team implemented concurrency within test
methods.  Note that, considering these four extra cases (ignored two
distributed CI cases), the usage of parallelization increases from
\percentParallel{} to \percentParallelUpdated{}.  We do not consider
this change significant enough to modify our conclusion about
practical adoption of parallelization (\numRQAdoptionOne{}).

%% , one runs a manually created Thread to run some
%% tests, and the other runs in parallel by using Java 8 collection
%% streams, that allows the developers to iterate over a list in
%% parallel.

%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.

>>>>

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, and we were unable to test
\SubjectsGithubNotTestable{} projects  due to incompatible environment
(\eg, missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
``flaky tests''~\cite{luo-etal-fse2014}.
In general, a ``flaky test'' is a test that either pass or fail under
the same circumstances leading to non-deterministic results.
\Comment{While there are several causes that may introduce randomness on test
results, our concern is on flakiness caused by
parallel execution.}
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with more than \SuiteFailingThreshold{} of tests failing to
reduce bias in our dataset.
We ignored failing tests with JUnit's
\CodeIn{@Ignore} annotation on the remaining projects.
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

@@

It is important to note that we under-estimated cost in our
experiments for one main reason.
Some projects may omit long-running tests on their default
execution. For instance, the project \CodeIn{apache.maven-surefire}
runs all unit tests in a few seconds.  According to our criteria, this
project is classified as \shortg{} but a closer look reveals
that only smoke tests are run by default in this project.
Time-consuming integration and system tests are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.
\Comment{
Although failing tests may introduce noise in our measurements, we
carefully eliminated subjects with more than \SuiteFailingThreshold{} of
test failures. 
}
From the \numSubjs{} testable projects, \numSubjsPass{} successfully
executed all tests and \numSubjsFail{} reported some test failure.
Furthermore, from these \numSubjsFail{} subjects, only 11 subjects
have more than 5\% of failing tests (7.3\% in average).
\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, nearly 1 in every 4
      projects) take at least 1 minute to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
measures the distribution of test costs in test suites as to estimate
potential of obtaining speedups with parallelization.  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions. X-axis
        denote projects appearing in arbitrary order.}%
\end{figure}

@@

%% Commented as we don't follow this pattern on the other RQs
\Comment{
Adoption concerns with the popularity of  parallelization schemes and
(\numRQAdoptionTwo) how developers involved in costly projects, not
using parallelization, perceive this technology.
}
\begin{itemize}
    \item \numRQAdoptionOne. \textbf{\RQAdoptionOne{}}
\end{itemize}

@@

which parallel configuration modes it uses to run the

@@

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\numProjectsPar{} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.

Table~\ref{tab:freqmodes-dynamic} shows the \numProjectsPar{} projects
we identified where parallelism is enabled by default in Maven.
Column ``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.
We note that, considering these projects, the modules that do not use
the configuration cited use the sequential configuration \Seq{}.
For example, three modules (=28-25) from Log4J2 use sequential
configuration.

\subsubsection{Static checking}
\label{sec:rqC-2}
As our previous approach cannot detect parallelism in non-default
configurations, we also looked for indication of parallelism in build
files\Comment{ in the same sample set of \numMedLong{} projects}.  We
parsed all \emph{pom.xml} files under the project's directory and used
the same approach as in our previous analysis to classify
configurations.  We noticed initially that our approach was unable to
infer the configuration mode for cases where the decision depends on
the input (\eg,
\CodeIn{<parallel>\$\{parallel.type\}</parallel>}). For these
projects, the tester needs to provide additional parameters in the
command line to enable parallelization (\eg, \CodeIn{mvn test
  -Dparallel.type=classesAndMethods}). To handle those cases, we
considered all possible values for the parameter (in this case,
\CodeIn{\$\{parallel.type\}}).  It is also important to note that this
approach is not immune to false negatives, which can occur when
\emph{pom.xml} files are encapsulated in jar files or files downloaded from
the network.  Consequently, this static checking is complementary to
the dynamic checking, previously presented.
This methodology founds \numProjectsParStatic{} projects.
Compared to the set of projects listed in
Table~\ref{tab:freqmodes-dynamic}, we found four new projects, namely:
\CodeIn{Google Cloud\Comment{ Platform} DataflowJavaSDK} (using
configuration \ParClassParMeth), \CodeIn{Mapstruct} (using configuration
\ForkSeq{}), \CodeIn{T-SNE-Java} (using configuration \ForkSeq), and
\CodeIn{Urbanairship Datacube} (using configuration \ParClassParMeth).
Curiously, we also found that project \CodeIn{Jcabi}, \CodeIn{Rultor},
and \CodeIn{Takes} were not detected using this methodology.
That happened because these projects loaded a \emph{pom.xml} file from
a jar file that we did not check.  Considering the static and dynamic
methods together, we found a total of \numProjectsParTotal{} distinct
projects using parallelism, corresponding to the union of the two
subject sets.

@@

\begin{enumerate}
\item How long does it take for tests to run in your environment? Can
  you briefly define your setup?
\item Do you confirm that your regression test suite does *not* run in parallel?
\item\label{questionThree} Select a reason for not using parallelization:
  \begin{enumerate}[label=\alph*)]
  \item I did not know it was possible
  \item I was concerned with concurrency issues
  \item I use a continuous integration server
  \item Some other reason. Please elaborate.
  \end{enumerate}
\end{enumerate}
%% \begin{enumerate}
%% 	\item How long does it take for test to run in your
%%		environment?
%%	\item Can you briefly define your setup?
%%	\item Do you confirm that your project does not run in
%%		parallel?
%%	\item Select a reason for not using paralellization:
%%		\begin{enumarate}
%%			\item I did not know it was possible;
%%			\item I was concerned with concurrency issues;
%%			\item I use a continuous integration server;
%%			\item Some other reason.
%%		\end{enumerate}
%% \end{enumerate}
%% One of the goals of the first questions is to identify potential
%% discrepancies between our experimental environment and the environment
%% of developers.  Overall, we found that \Fix{...}

Considering question 1, we confirmed that execution time was
compatible with the results we reported in Section~\ref{sec:rqA}.
Furthermore, \emailsCI{} of the participants indicated the use of
Continuous Integration (CI) to run tests, with \emailsDistributed{} of
these participants reporting that test suites are modularized and
those modules are tested independently in CI servers through different
parameters.  Those participants explained that such practice helps to
reduce time to observe test failures, which is the goal of speeding up
regression testing.  A total of \emailsLocal{} participants answered
that they do run tests in their local machines.  Note, however, that
CI does not preclude low-level parallelization.  For example,
installations of open-source CI tools (\eg{}, Jenkins~\cite{jenkins})
in dedicated servers would benefit from running tests faster through
low-level test suite parallelization.
% \emailsNotDescribed{} developers did not described their environment.

Considering question 2, the answers we collected indicated, to our
surprise, that six of the \emailsProjectsAnswered{} projects execute
tests in parallel.  This mismatch is justified by cases where neither
of our checks (static or dynamic) could detect presence of
parallelism.  A closer look at these projects revealed that one of
them contained a \emph{pom.xml} file encapsulated in a jar file
(similar case as reported in Section~\ref{sec:rqC-2}), in one of the
projects the participant considered that distributed CI was a form of
parallelism, and in four projects the team preferred to implement
parallelization instead of using existing features from the testing
framework and the build system~---~in two projects the team
implemented concurrency control with custom JUnit test runners and in
two other projects the team implemented concurrency within test
methods.  Note that, considering these four extra cases (ignored two
distributed CI cases), the usage of parallelization increases from
\percentParallel{} to \percentParallelUpdated{}.  We do not consider
this change significant enough to modify our conclusion about
practical adoption of parallelization (\numRQAdoptionOne{}).
%% , one runs a manually created Thread to run some
%% tests, and the other runs in parallel by using Java 8 collection
%% streams, that allows the developers to iterate over a list in
%% parallel.
%% did not confirmed, however,
%% the developers confirmed the need of an extra parameter at the command
%% line to execute in parallel.
